Approximation as Differentiation notes

### 2025-02-21 notes/definitions.tex
Bilinearity.

$\CMon$ is the category whose objects are the commutative monoids $M$ and morphisms $M \to M'$ are the
commutative monoid homomorphisms. $\CMon$ is symmetric closed monoidal, with the trivial one-element monoid
$\One$ as terminal object and tensor product $M \tensor M'$ given by the direct product of $M$ and $M'$. In
fact $\CMon$ is complete and cocomplete, inheriting all limits and colimits from $\Set$.

@@

A category is $\CMon$-enriched if every $\Hom{A}{B}$ is a commutative monoid with the \emph{zero} morphism
$\zero_{A,B}$ and addition of morphisms $+_{A,B}$ as the commutative monoid operations, and composition
is a commutative monoid homomorphism.

@@

\begin{minipage}[t]{0.45\textwidth}
\begin{center}
\begin{salign*}
   p_A \after i_A &= \id_A \\
   p_B \after i_A &= \zero_{A,B}
\end{salign*}
\end{center}
\end{minipage}%
\begin{minipage}[t]{0.45\textwidth}
\begin{center}
\begin{salign*}
   p_B \after i_B &= \id_B \\
   p_A \after i_B &= \zero_{B,A}
\end{salign*}
\end{center}
\end{minipage}

@@

\begin{salign*}
i_A \after p_A + i_B \after p_B &= \id_{A \oplus B}
\end{salign*}

>>>>

$\CMon$ is the category whose objects are the commutative monoids $M$ and morphisms $M \to M'$ are the
commutative monoid homomorphisms. $\CMon$ is symmetric closed monoidal, with the trivial one-element monoid
$\One$ as terminal object and monoidal product $M \tensor M'$ given by the direct product of $M$ and $M'$.
$\CMon$ is complete and cocomplete, inheriting all limits and colimits from $\Set$.

@@

A category $C$ is \emph{$\CMon$-enriched} if every hom-object $\Hom{C}{A}{B}$ is a commutative monoid with a
\emph{zero} morphism $\zero_{A,B}$ and addition of morphisms $+_{A,B}$ as the commutative monoid operations,
and composition is a morphism $\Hom{C}{B}{C} \tensor \Hom{C}{A}{B} \to \Hom{C}{A}{C}$ in $\CMon$,
i.e.~satisfies

\begin{salign*}
(f + g) \comp h &= (f \comp h) + (g \comp h) \\
h \comp (f + g) &= (h \comp f) + (h \comp g)
\end{salign*}

@@

\begin{minipage}[t]{0.45\textwidth}
\begin{center}
\begin{salign*}
   p_A \comp i_A &= \id_A \\
   p_B \comp i_A &= \zero_{A,B}
\end{salign*}
\end{center}
\end{minipage}%
\begin{minipage}[t]{0.45\textwidth}
\begin{center}
\begin{salign*}
   p_B \comp i_B &= \id_B \\
   p_A \comp i_B &= \zero_{B,A}
\end{salign*}
\end{center}
\end{minipage}

@@

\begin{salign*}
i_A \comp p_A + i_B \comp p_B &= \id_{A \oplus B}
\end{salign*}
